Multi sky-view\\ 3D aerosol distribution recovery

### 2013-08-04 article.tex
modifications by yoav

We focus on situations where, in addition to air molecules, there is a
single type of aerosol over a scene. Hence, the three-element vector
$[{\sigma}^{\rm aerosol},\varpi^{\rm aerosol},g]$ is uniform across
the scene, but the density distribution ${\DistUnknown}$ is
variable. As a numerical approximation, assume that within any voxel,
the molecular parameters $\{ \beta^{\rm air}(k),\alpha^{\rm air}(k)\}$
and the aerosol density $n(k)$ are constants, e.g., corresponding to
the value at each voxel center.  Following \cref{eq:tau}, the optical
depth between the TOA and voxel $k$ is
% \begin{equation}
%  \tau_{\rm SR}(k)= \sum_{q \in[{\rm SR},k]} \beta(q) l_{\rm SR}(q) \;\;.
%  \label{eq:lSRn}
%\end{equation}
\begin{equation}
  \tau_{\rm SR}(k)=
  \sum_{q \in[{\rm SR},k]}
  [\beta^{\rm air}(q)+\sigma^{\rm aerosol} n(q)] l_{\rm SR}(q)
  =\tau_{\rm SR}^{\rm air}(k)+  \sigma^{\rm aerosol}\sum_{q \in[{\rm SR},k]} l_{\rm SR}(q) n(q)
  ,
  \label{eq:lSRn}
\end{equation}
where $\tau_{\rm SR}^{\rm air}(k)=\sum_{q \in[{\rm SR},k]}\beta^{\rm
  air}(q)l_{\rm SR}(q)$.  Let $\vect{\tau}_{\rm SR}$ and
$\vect{\tau}_{\rm SR}^{\rm air}$ be column stack vector
representations of $\tau_{\rm SR}(k)$ and $\tau_{\rm SR}^{\rm
  air}(k)$, respectively. Then, we can write \cref{eq:lSRn} using
matrix notation: \mbox{$\vect{\tau}_{\rm SR}=\vect{\tau}_{\rm SR}^{\rm
    air} + \sigma^{\rm aerosol}\OpDistance^{\mathrm{Sun \rightarrow
      voxel}} {\DistUnknown}$}.

A similar analysis yields the optical depth along a LOS to voxel $k$,
$\tau_{{\rm LOS}_c}(k)$. It is expressed by element $k$ of
\mbox{$\vect{\tau}_{{\rm LOS}_c}=\vect{\tau}_{{\rm LOS}_c}^{\rm air} +
  \sigma^{\rm aerosol}\OpDistance^{\mathrm{voxel \rightarrow cam}}
  {\DistUnknown}$}.  The SR and LOS paths joining at each voxel can
form a single path from the TOA to camera $c$, yielding
\begin{equation}
  {\bm D}_c=
  {\bm D}^{\mathrm{Sun \rightarrow voxel}}+
  {\bm D}^{\mathrm{voxel \rightarrow cam}}_c
  \quad\text{ and }\quad
  \vect{\tau}_c=
  \vect{\tau}_{\rm SR}+
  \vect{\tau}_{{\rm LOS}_c}
  \;\;.
  \label{eq:D_tau_total}
\end{equation}
Hence, in matrix notation, \cref{eq:tau} yields the total optical
depths corresponding to LOSs (of camera $c$) and SRs that cross all
voxels:
\begin{equation}
  \vect{\tau}_c= \vect{\tau}_c^{\rm air}
  + \sigma^{\rm aerosol} {\bm D}_c {\bm n}
  \;\;.
  \label{eq:tautotal}
\end{equation}

@@

\section{Conclusions}
\label{sec:conclusions}

We describe a new way to sense the 3D atmosphere. We show feasibility
of departing from common 1D aerosol distribution models, in favor of
detailed 3D analysis.  The paper describes both a novel data
acquisition system concept for this recovery task, and a dedicated
algorithm for reconstructing aerosol distributions.

Even without regularization, the reconstruction algorithm handles
arbitrary density distributions. Using more prior knowledge,
e.g. spatial smoothness will improve the recovery.  The algorithm uses
a single scattering model. This approximation is valid when the
optical depth is small, which is common. To handle dense atmospheric
conditions (smoke, clouds), multi-scattering must be incorporated.

The goal, of coarse, is to deploy such a system on a very large
scale. However, it must be first ensured that camera units are both
cost effective and field-robust, and that their positioning density is
proper. This will require a long-term engineering effort. Camera
specifications should be set to optimally recover a wide range of
aerosol distributions. This requires a major theoretic and numerical
research and development phase.  The new sensing modality and object
of interest offer a new domain for computational photography
problems. For example, how can compressed sensing principles be
employed here? How can priors be used to make data acquisition more
efficient? How can such a system be calibrated over time? Many such
questions and solutions would rise.

@@

We thank Anthony~B. Davis and David~J. Diner for useful
discussions. Yoav Schechner is a Landau Fellow - supported by the Taub
Foundation. This work was conducted in the Ollendorff Minerva
Center. Minerva is funded through the BMBF.

>>>>

We focus on situations where, in addition to air molecules, there is a
single type of aerosol over a scene. Hence, the three-element vector
$[{\sigma}^{\rm aerosol},\varpi^{\rm aerosol},g]$ is uniform across
the scene, but the density distribution ${\DistUnknown}$ is
variable. As a numerical approximation, assume that within any voxel,
the molecular parameters $\{ \beta^{\rm air}(k),\alpha^{\rm air}(k)\}$
and the aerosol density $n(k)$ are constants, e.g., corresponding to
the value at each voxel center.  Following \cref{eq:tau}, the optical
depths between the TOA and voxel $k$, and from voxel $k$ to camera $c$ are
% \begin{equation}
%  \tau_{\rm SR}(k)= \sum_{q \in[{\rm SR},k]} \beta(q) l_{\rm SR}(q) \;\;.
%  \label{eq:lSRn}
%\end{equation}
\begin{align}
  \tau_{\rm SR}(k)&=
  \sum_{q \in[{\rm SR},k]} l_{\rm SR}(q)
  [\beta^{\rm air}(q)+\sigma^{\rm aerosol} n(q)] \\
  \tau_{{\rm LOS}_c}(k)&=
  \sum_{m \in[{\rm SR},k]} l_{{\rm LOS}_c}(m)
  [\beta^{\rm air}(m)+\sigma^{\rm aerosol} n(m)].
  \label{eq:lSRn}
\end{align}
Let $\vect{\tau}_{\rm SR}$ and $\vect{\beta}^{\rm air}$ be 
column stack vector
representations of $\tau_{\rm SR}(k)$ and $\beta^{\rm air}(k)$, respectively.
 Then, we can write \cref{eq:lSRn} using
matrix notation: 
   \mbox{$\vect{\tau}_{\rm SR}=
   \OpDistance^{\mathrm{Sun \rightarrow voxel}}\vect{\beta}^{\rm air} 
   + \sigma^{\rm aerosol}\OpDistance^{\mathrm{Sun \rightarrow voxel}} {\DistUnknown}$},\
and
    \mbox{$\vect{\tau}_{{\rm LOS}_c}=
   \OpDistance^{\mathrm{voxel \rightarrow cam}}\vect{\beta}^{\rm air}
   + \sigma^{\rm aerosol}\OpDistance^{\mathrm{voxel \rightarrow cam}} {\DistUnknown}$}.
The SR and LOS paths joining at each voxel 
form a single path from the TOA to camera $c$.  
Hence, in matrix notation, \cref{eq:tau} yields the total optical
depths corresponding to LOSs (of camera $c$) and SRs that cross all
voxels:
\begin{equation}
  \vect{\tau}_c= \vect{\tau}_c^{\rm air}
  + \sigma^{\rm aerosol} {\bm D}_c {\bm n}
  \;\;,
  \label{eq:tautotal}
\end{equation}
where   ${\bm D}_c=
  {\bm D}^{\mathrm{Sun \rightarrow voxel}}+
  {\bm D}^{\mathrm{voxel \rightarrow cam}}_c$
and $\vect{\tau}_c^{\rm air}= {\bm D}_c \vect{\beta}^{\rm air}$.

%
%
%and
%$\vect{\tau}_{\rm SR}^{\rm air}$ be column stack vector
%representations of $\tau_{\rm SR}(k)$ and $\tau_{\rm SR}^{\rm
%  air}(k)$, respectively.
%
%A similar analysis yields the optical depth along a LOS to voxel $k$,
%$\tau_{{\rm LOS}_c}(k)$. It is expressed by element $k$ of
%\mbox{$\vect{\tau}_{{\rm LOS}_c}=\vect{\tau}_{{\rm LOS}_c}^{\rm air} +
%  \sigma^{\rm aerosol}\OpDistance^{\mathrm{voxel \rightarrow cam}}
%  {\DistUnknown}$}.  The SR and LOS paths joining at each voxel can
%form a single path from the TOA to camera $c$, yielding
%\begin{equation}
%  {\bm D}_c=
%  {\bm D}^{\mathrm{Sun \rightarrow voxel}}+
%  {\bm D}^{\mathrm{voxel \rightarrow cam}}_c
%  \quad\text{ and }\quad
%  \vect{\tau}_c=
%  \vect{\tau}_{\rm SR}+
%  \vect{\tau}_{{\rm LOS}_c}
%  \;\;.
%  \label{eq:D_tau_total}
%\end{equation}
%Hence, in matrix notation, \cref{eq:tau} yields the total optical
%depths corresponding to LOSs (of camera $c$) and SRs that cross all
%voxels:
%\begin{equation}
%  \vect{\tau}_c= \vect{\tau}_c^{\rm air}
%  + \sigma^{\rm aerosol} {\bm D}_c {\bm n}
%  \;\;.
%  \label{eq:tautotal}
%\end{equation}

@@

\section{Discussion}
\label{sec:conclusions}

We describe a way to sense the 3D atmosphere. It can help 
remote sensing departing from common 1D aerosol distribution models, in favor of detailed 3D RT analysis.  The paper describes both a novel data
acquisition system concept for this recovery task (ground-based camera network), and a dedicated algorithm for reconstructing aerosol distributions. Using more prior knowledge on the nature of distributions will improve the recovery.  The estimation algorithm uses a single scattering model. This approximation is valid when the
optical depth is small. However, as the MC simulation show, it is important to generalize this algorithm so that it explicitly incorporates high-order scattering in the scene, including the ground. This will certainly be needed for dense distributions as clouds.

To deploy such a system on a very large scale will require a long-term engineering effort. Camera specifications should be set to optimally recover a wide range of
aerosol distributions. This requires a major theoretic and numerical
research.

@@

We thank David~J. Diner for useful
discussions. Yoav Schechner is a Landau Fellow - supported by the Taub
Foundation. This work was conducted in the Ollendorff Minerva
Center. Minerva is funded through the BMBF.
